\documentclass{report}
\usepackage{outline}
\usepackage{geometry}[1in]
\pagestyle{empty}

\begin{document}

\begin{outline}
  \item {\bf Introduction }
  \begin{outline}
    \item Usefulness of crowdsourced geographic information in flood research in general.
    \item Remotely sensed image versus crowdsourced images.
    \item What is flood water segmentation and and its challenges?
  \end{outline}
    \item {\bf Related Work \& Contributions}
    \begin{outline}
	    \item Present Witherow paper and why such approach is bad in practice.
	    \item {\bf Thesis:} Flood water segmentation is possible from just a single image and without any 						 assumptions on the crowdsourced flood image
	    \item Summarize the paper structure.
    \end{outline}
    \item {\bf Flood Water Segmentation}
    \begin{outline}
	    \item Detail the goal of image processing and computer vision algorithms for this problem.
	    \item {\bf Horizon Line Detection for Flood Images}
	    	\begin{outline}
			    \item What is HLD? How has it been applied?
			    \item {\bf Edged-based HLD}
			    \begin{outline}
			    	\item {\bf Algorithm}: Edge detection with Hough transformation
			    \end{outline}
			    \item {\bf Drawbacks of Edged-based HLD}
			    \begin{outline}
			    	\item Does not work if water horizon is not the most prominent edge.
				\item Example image with problem.
				\item Not applicable to nonlinear water horizon unless you employ fancier methods.
			    \end{outline}
			    \item {\bf Region-based HLD}
			    \begin{outline}
			    	\item Briefly discuss what is region-based HLD and define superpixels
				\item {\bf Algorithm}: SLIC/SLICO
			    \end{outline}
			    \item {\bf Drawbacks of Region-based HLD}
			    \begin{outline}
			    	\item Number of clusters to set is unclear and can have widely different results.
				\item Specularity is a big problem.
				\item Example image with problem.
			    \end{outline}
			    \item {\bf Semantic Segmentation for Flood Images}
			    \begin{outline}
			    	\item What is the current state-of-the-art approach in computer vision for segmentation?
				\item What is convolutional neural networks (CNN) and how it is different from the 						  traditional approach?
				\item {\bf Algorithm}: Fully Convolutional Neural Network (FCN) trained on PASCAL-Context
			    \end{outline}
			    \item {\bf Improving FCN Approach}
			    \begin{outline}
			    	\item Transfer learning and finetuning on labeled flood images
			    \end{outline}
		\end{outline}
    \end{outline}
    \item {\bf Conclusion}
    \item {\bf References}
\end{outline}

\end{document}